Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-18 doc/manuscript/manuscript.Rmd
Updated acknowledgements

The authors would like to thank Rebecca Higgens for providing valuable insights
into the historical context of the data collection and curation. Funding for
this research was provided by the North Central Soybean Research Program
(#639K623), a Layman Award (#2446), and start-up funds from the University of
Nebraska-Lincoln.

>>>>

The authors would like to thank Rebecca Higgens for providing valuable insights
into the historical context of the data collection and curation. Funding for
this research was provided by the North Central Soybean Research Program
(#639K623) to SEE, a Layman Award (#2446) to SEE, USDA-ARS National Sclerotinia
Initiative (#58-5442-2-209) to JRS/SEE, and start-up funds from the University of
Nebraska-Lincoln to SEE.
